Adaptive evolution with aneuploidy and mutation

### 2022-03-07 ms/ms.tex
added missing parentheses

Second, we performed simulations without mutations from $\euwt$ to $\eumt$ (\Cref{fig:no direct mut}). 
% TODO MP: I comment this out - not clear what "Before" refers to, and not sure we need this sentence. what do you think?
%Before, we had the optimal scenario of waiting until the first successful mutation appears and then waiting until is reaches fixation. Our approximations did quite well there. 
Here, aneuploidy is transient and fixation of \anwt\ or \anmt\ could be outpaced by the arrival of the next genotype. This would explain the discrepancy between the green curves in \Cref{fig:no direct mut}.
To asses this further, \Cref{fig:fixT vs waitT} provides a clear picture. At least for intermediate to high values of the respective range of the parameters, the waiting time until a new genotype appears and does not go to extinction is far shorter compared  to waiting time for fixation of the previous genotype. Taking this into account, it seems reasonable to ignore the fixation time of $\anwt$ and $\anmt$, which results in a better fit between our approximation and simulation results (red curves in \Cref{fig:no direct mut}, although still an overestimation.
% TODO MP : not sure we should say this without explaining why x=0.017. did we use 0.95 in the approximation or not?
% Inferring $x=0.017$ for $\tilde{T}_{\anmt \rightarrow \eumt}$ to get the best fit in panel B, does not imply that it is also a best fit for panels A and C. However, we stop simulations in state $\eumt$ if they have frequency $0.95$. 
The discrepancies in \Cref{fig:no direct mut}C seem to be particularly odd as the approximations are nearly constant whereas the average time from simulations decreases log-linearly with the aneuploidy rate, $\delta$.

>>>>

Second, we performed simulations without mutations from $\euwt$ to $\eumt$ (\Cref{fig:no direct mut}). 
% TODO MP: I comment this out - not clear what "Before" refers to, and not sure we need this sentence. what do you think?
%Before, we had the optimal scenario of waiting until the first successful mutation appears and then waiting until is reaches fixation. Our approximations did quite well there. 
Here, aneuploidy is transient and fixation of \anwt\ or \anmt\ could be outpaced by the arrival of the next genotype. This would explain the discrepancy between the green curves in \Cref{fig:no direct mut}.
To asses this further, \Cref{fig:fixT vs waitT} provides a clear picture. At least for intermediate to high values of the respective range of the parameters, the waiting time until a new genotype appears and does not go to extinction is far shorter compared  to waiting time for fixation of the previous genotype. Taking this into account, it seems reasonable to ignore the fixation time of $\anwt$ and $\anmt$, which results in a better fit between our approximation and simulation results (red curves in \Cref{fig:no direct mut}), although still an overestimation.
% TODO MP : not sure we should say this without explaining why x=0.017. did we use 0.95 in the approximation or not?
% Inferring $x=0.017$ for $\tilde{T}_{\anmt \rightarrow \eumt}$ to get the best fit in panel B, does not imply that it is also a best fit for panels A and C. However, we stop simulations in state $\eumt$ if they have frequency $0.95$. 
The discrepancies in \Cref{fig:no direct mut}C seem to be particularly odd as the approximations are nearly constant whereas the average time from simulations decreases log-linearly with the aneuploidy rate, $\delta$.
